\subsection{Presentation of the problem}
In this section, we are going to generalize the model a little bit. Up to this point, we have considered that each link has a known capacity and that this quantity is exact. This is, however, not true in general. We can expect the actual capacities to be close to the numbers given but we should take into account that they can fluctuate around those values. Our new model will thus have to deal with this uncertainty. Because the value of the capacities can be considered as an unknown parameter, we will use stochastic programming.

We also know that the 50 Gbit/s-demand can be rerouted after the actual values are known but the 40 Gbit/s-demand must be determined on beforehand (and thus not cannot be rerouted after knowing the actual capacities).

\subsection{Mathematical model}
Just as in the previous models, we introduce the set $I$ :
$$I = \{ Sto,Lon,Ber,War,Par,Rom,Mad\}$$

The main difference with previous models is the presence of uncertainty. As usual, we will handle this by discretizing this uncertainty into different scenarios $s$ with an associated probability $p_s$. Each scenario corresponds to a complete set of known capacities. We can for example say that the second scenario is the one where the capacities are exactly those given. The scenarios and the corresponding probabilities must be chosen beforehand and have an influence on the solution. We can intuitively say that if the scenarios do not vary much with respect to the mean, the solution will not vary much either. On the other hand, if at least one scenario is very different from the mean values given, we can expect a quite different solution. In this section, we assume that the set of scenarios are given. The results section presents the set of scenarios chosen by our group but it can easily be changed.

Let us assume that we have $S$ scenarios and define the parameters : 
\begin{align*}
&c_{i,j,s} &\text{capacity in scenario $s$ between cities $i$ and $j$} \\
& &i,j \in I \text{ and } s=1,...S
\end{align*}

For every scenario, we also introduce the variable $maxUtility_s$, the maximum utility in scenario $s$. It is clear that those variables must lie between 0 and 1.

Our goal is to minimize the expected value of the maximum utility. Since scenario $s$ has probabily $p_s$, we have that our objective function is :
$$\sum_{s=1}^S p_s\: maxUtility_s$$

Let us also introduce the variables $x$, depicting the 40 Gbit/s-flow. Because this flow must be determined on beforehand, it cannot depend on the scenarios.
\begin{align*}
&x_{i,j} &\text{flow in Gbit/s going from $i$ to $j$ for the 40 Gbit/s-flow}\\
& &i,j \in I
\end{align*}

All $x$ are positive. Similarly, let us define the variables $y$ for the 50 Gbit/s-flow. This can be rerouted and thus we could potentially have different flows for different scenarios.
\begin{align*}
&y_{i,j,s} &\text{flow in Gbit/s going from $i$ to $j$ for the 50 Gbit/s-flow and scenario $s$}\\
& &i,j \in I \text{ and } s=1,...,S
\end{align*}

Here also, all $y$ are positive. Just as previously, the first constraint to think about is the conservation of flow. If we think about London as a source and Warsaw as a sink, we have, for the 40 Gbit/s-flow : 
$$\sum_{j\in I} x_{i,j} - \sum_{j\in I}x_{j,i} = b_i = \begin{bmatrix}
  b_{Sto}\\
  b_{Ber}\\
  b_{War}\\
  b_{Lon}\\
  b_{Par}\\
  b_{Mad}\\
  b_{Rom}
 \end{bmatrix} =
 \begin{bmatrix}
  0\\
  0\\
  -40\\
  40\\
  0\\
  0\\
  0
 \end{bmatrix}$$
 
 This must hold for every scenario since we cannot reroute this traffic. Concerning the 50 Gbit/s-flow, the conservation equation is given by : 
 $$\sum_{j\in I} y_{i,j,s} - \sum_{j\in I}y_{j,i,s} = a_i = \begin{bmatrix}
  a_{Sto}\\
  a_{Ber}\\
  a_{War}\\
  a_{Lon}\\
  a_{Par}\\
  a_{Mad}\\
  a_{Rom}
 \end{bmatrix} =
 \begin{bmatrix}
  50\\
  0\\
  0\\
  0\\
  0\\
  0\\
  -50
 \end{bmatrix}$$
 
 The other constraint is that the amount of flow cannot exceed the capacity. As stated above, we have a given capacity for each scenario. Because we know that the maximum utility is not larger than 1 and that we are minimizing a weighted sum of the maximum utilities, we have the following constraint :
 
 $$x_{i,j}+x_{j,i}+y_{i,j,s}+y_{j,i,s} \leq maxUtility_s \: c_{i,j,s}$$
 
 This equation must hold for every $i,j \in I$ and every scenario $s=1,...,S$ because we do not want to find ourselves in a position where we cannot route the traffic.
 
 We now have everything we need and can state the full mathematical model.
 
 \begin{align*}
 &\min_{x,y,maxUtility} \quad \sum_{s=1}^S p_s \: maxUtility_s &\\
 &s.t. \quad maxUtility_s \leq 1 &s=1,...,S\\
 &\quad\quad \sum_{j\in I}x_{i,j} - \sum_{j\in I}x_{j,i} = b_i &i\in I\\
 &\quad\quad \sum_{j\in I}y_{i,j,s} - \sum_{j\in I}y_{j,i,s} = a_i &i\in I,s=1,...,S\\
 &\quad\quad x_{i,j}+x_{j,i}+y_{i,j,s}+y_{j,i,s} \leq maxUtility_s \: c_{i,j,s} &i,j\in I , s=1,...,S\\
 &\quad\quad x_{i,j} \geq 0 & i,j\in I\\
 &\quad \quad y_{i,j,s} \geq 0 & i,j\in I, s=1,...,S
 \end{align*}
 
 We can note that we do not need to add the positivity constraint for $maxUtility_s$ because the fourth constraint already demands it (because $x$,$y$ and $c$ are all positive).
 
 We can also note that if the problem does not have a feasible region, it means that, at least in one of the scenario, it is not possible to route the traffic.



 